---
title: "Data Management Project"
author: Joséphine Laguardia and Lucile Dubarry
format: html
code-fold: true
echo: false
---

```{r}
#| message: false
here::i_am("LAGUARDIA_DUBARRY.Rproj")
library(ggplot2)
library(dplyr)
library(tidyr)
library(vroom)
library(here)
```

```{r}
#| message: false
museum <- vroom(here("musees-de-france-base-museofile.csv"))
freq <- vroom(here("frequentation-des-musees-de-france.csv"))
```

## Link to Github

We work on the Github project, available [here](https://github.com/luciledubarry/LAGUARDIA_DUBARRY.git).

## Sources

Both our data sets come from the **French Ministry of culture**. Since 2011, the Ministry of culture has set up both a public data census service and a data sharing service, open to all citizens, researchers, students, journalists, and companies. Its aim is to improve the exposure of cultural works and French cultural institutions. Even though it is a legal obligation since 2018 for administrations to open up their data, there are a lot of benefits from sharing these data: full transparency with the citizens, support for social innovations, boosting the local economy through discovering local cultural institutions, boosting France international influence etc.

Our first data set, **"Musées de France: base Muséofile"**, features all the museums that have been given the "Musée de France" label by the *Code du Patrimoine*. A "Musée de France" is, in accordance with the *Code du Patrimoine*, a "permanent collection made up of items whose conservation and presentation are of public interest, and organized for the knowledge, education and enjoyment of the public". As we'll see later, it contains basic information on these museums (such as the address, the website or the year of creation), as well as interesting complementary characteristics (such as the main theme of the museum, its most important asset or the leading artist of its permanent collection).

Our second data set, **"Fréquentation des musées de France"**, contains the number of visitors each year, from 2001 to 2021.

The advantage of gathering databases from the same website and the same institution of origin is that the merging will be a lot easier, due to the fact that they have variables in common. What's more, the source being the Ministry of culture gives us the assurance that the data has been collected correctly.

The **"Musées de France: base Muséofile"** dataset is available [here](https://www.data.gouv.fr/fr/datasets/musees-de-france-base-museofile/#/resources)

The **"Fréquentations des musées de France"** dataset is available [here](https://www.data.gouv.fr/fr/datasets/frequentation-des-musees-de-france-1/#/resources)

## Short description of the data files

In this table, you'll find some basic information about our first data file **"Musées de France: base Muséofile"**.

```{r}
#| message : false 
info_museum <- museum |>
  summarise(NROW(museum),NCOL(museum))
knitr::kable(info_museum, format = "html",col.names = c("Number of rows (number of museums","Number of columns (characteristics)"))
```
In this other table, you'll find the same basic information for our second data file **"Fréquentations des musées de France"**.
```{r}
info_freq <- freq |>
  summarise(NROW(freq), NCOL(freq))
knitr::kable(info_freq, format = "html",col.names = c("Number of rows", "Number of columns"))
```

## Description of each variable

### 1st data set - Musée de France: base Muséofile:
REF : Muséofile reference code; 

NOMOFF : Official name of the museum; 

AUTNOM : Customary name of the museum;

ADRL1_M : Address; 

LIEU_M : Specifications of the address; 

CP_M : Postal code;

VILLE_M : City;

DPT : Department;

REGION : Region;

URL_M : Website or page address;

TEL_M : Phone number of the museum;

CATEG: Specific museum category;

DOMPAL: Main themes of the collections; 

HIST: History of the collection; 

ATOUT: Assets of the collection; 

THEMES: Details of the themes  of the collections; 

ARTIST: Leading artists of the collection; 

PHARE: Leading personalities of the collection;

INTERET: Architectural feature of the building;

PROT-BAT: Type of building preservation;

PROT-ESP: Type of space preservation;

REFMER: Reference code in the Mérimée database;

AN-CREAT: Year of creation;

DMAJ: Date of the last information update; Latitude; Longitude.

### 2nd data set - Fréquentation des musées de France:
REF_MUSEE: Museum reference code; 

NOM_DU_MUSEE: Museum official name; 

ANNEE: Year of update; 

REGIONS: Region;

VILLE: City;

DATE_APPELLATION: Date on which controlled museums receive the designation “Musées de France”, since February 2003

PAYANT: Number of visits with paid entrance ticket;

GRATUIT: Number of visits with free entrance ticket;

TOTAL: Total of number of visits (PAYANT + GRATUIT);

NOTE: indicates: 

- "F": the museum is closed; 

- "NC": no frequentation data have been provided; 

- "R": withdrawal of the "Musées de France" designation.

ID_MUSEOFILE: Muséofile reference code ; 

NOMDEP: Department;

OBSERVATIONS: The "OBSERVATIONS" column contains the references of the museums whose frequentation is aggregated.

## Data cleaning and joining

### Year of interest: 2019

The freq data set only includes Muséofile references starting from 2019. The years following 2019 are highly impacted by Covid crisis. We don't take into account these years in our study, as they are not representative of the museum's usual frequentation. 

We use the “filter” function and select only the year **2019** for the freq data base.

```{r}
freq <- freq |> filter(annee == 2019)
```

### Selecting variables of interest

First, we get rid of museums that don't have the frequentation data, represented by the variable NOTE (when either the museum is closed or the information is partially completed). 

So, we only select the museums whose NOTE variable is empty. 

```{r}
freq <- freq |> filter(is.na(note))
```

Then, we only keep the variables of interest, and drop the rest. The variables that we keep are:

**1st data set Frequentation:**

ID_MUSEOFILE; 
NOM_DU_MUSEE; 
REGIONS; 
VILLE; 
TOTAL; 
PAYANT; GRATUIT
NOMDEP

**2nd data set Muséofile:**

REF;
DOMPAL;
ARTISTE;
PROT-ESP; PROT-BAT;
LATITUDE; LONGITUDE

```{r}
freq <- freq |> select(id_museofile, nom_du_musee, regions, ville, total, payant, gratuit, nomdep)
museum <- museum |> select(ref, dompal, artiste, prot_bat, prot_esp, latitude, longitude)
```

### Data joining

We join the data bases with reference to the **Muséofile ID number**. On the Museofile database it is the variable named REF and on the Frequentation database it is the variable named ID_MUSEOFILE.

We use the function "inner_join" as it allows us to keep only the museums for which we have all the information (the frequentation and the characteristics). 

```{r}
# first, they have to have the same variable name
museum <- museum |> rename(id_museofile = ref)
# now we can do the joining
data <- inner_join(freq, museum, by = 'id_museofile')
```

## Description of the research questions

**I.	Why this choice of topic?**

The selection of the research topic on museum frequentation in France stems from an interest in understanding the current landscape of museums in the country. Exploring the dynamics of museum frequentation is crucial for gaining insights into the factors influencing visitor numbers. The central question revolves around the present state of museums in France and the key characteristics that impact their attendance. 
We want to put into perspective the link between museums’ frequentation and museums’ characteristics, whether it be their location, their category (history, art, etc…), or their main asset (the most famous artist in their collection for example). Do historical museums attract more visitors than art ones? Is a particular art theme more popular in France? Are the assets of a museum more important than its location when it comes to frequentation?

**II.	Main research axes based on the selected key variables**

The research will focus on several key factors. 

1.	Firstly, we will study the **diversity** of museum themes in France, aiming to identify potential preferences among the public for specific thematic content. This will involve calculating cumulative frequentation figures for each theme. 

2.	Secondly, we will analyze the **geographical distribution** of museums in France, categorizing regions based on cultural vitality, considering both the number of museums and attendance figures.

3.	Additionally, we will study the primary collections and standout artists featured in each museum, and determine if this **asset** influences the frequentation of the museum. 

Because of a lack of data, a year-by-year comparison of attendance is impossible, as the dataset only includes Muséofile references starting from 2019.

**III.	Expected results**

The research will employ various methods to synthesize a comprehensive overview of the current museum landscape in France. This includes creating a visual representation, such as a map of France, depicting the number of museums, different thematic categories, and cumulative attendance figures by region. 

Furthermore, the study aims to identify the primary factors contributing to museum attendance, expressing it conditionally through three key variables: location, theme, and collection. The expected results include a concrete understanding of the factors shaping museum frequentation, providing valuable insights for both cultural institutions and policymakers in France.

## Graphical representation

Here are all the museums of France on an interactive map, where we can get the name of the museum by clicking on the marker.
```{r}
#| message: false
library(leaflet)
```

```{r}
leaflet(data = data) %>% addTiles() %>%
  addMarkers(~longitude, ~latitude, popup = ~as.character(nom_du_musee))
```
There are a lot of markers at first, but it becomes clearer and clearer as we zoom in. 
This is not a perfect representation, but it is a first. As we continue our project, we will try to represent the density of museums by region or by department.

